Covariate Analysis of ROSMAP Reprocessed counts Regressing out Diagnosis as well for TWAS

### 2019-09-19 code/Ancestry_PCA-copy.Rmd
Final Regress

## Pull 1000Genomes down and process
* Pull out reference populations (CEU, YRI, CHB, JPT)
```{bash pull_1000Genomes, echo=FALSE}
CORES=$(nproc)

#ID Sample list of needed Ref Populations
wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/integrated_call_samples.20101123.ALL.panel

@@

for i in {1..22}
do
    wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr1.integrated_phase$i\_v3.20101123.snps_indels_svs.genotypes.vcf.gz
     wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr1.integrated_phase$i\_v3.20101123.snps_indels_svs.genotypes.vcf.gz.tbi
    #tabix -p vcf chr$i\.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz
done

>>>>

## Pull 1000Genomes down and process
* Pull out reference populations (CEU, YRI, CHB, JPT)
```{bash pull_1000Genomes, echo=FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/plink-1.07-x86_64/

CORES=`expr $(nproc) - 2`

#ID Sample list of needed Ref Populations
wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/integrated_call_samples.20101123.ALL.panel

ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/

@@

#i=22
for i in {1..22}
do
	wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz

    gunzip ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
    rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf

done

#Merge All Plink Files into genome wide
for i in {2..22}
do
  echo 1000Genomes_chr$i >> Merge.List
done

### 2019-09-19 code/MSBB_RegressDiagnosis_4_TWAS.Rmd
Final Regress

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, cache=FALSE}
##It is assumed your working directory is "~/ampad-DiffExp/gene_level_analysis"
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(glmnet)
library(synapser)
library(knitr)
library(doParallel)
library(foreach)
cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
# Source modified utility functions from limma and sva package
source('../utilityFunctions/parallelDuplicateCorrelation.R')
source('../utilityFunctions/irwsva.build.R')
source('../utilityFunctions/f.pvalue.R')
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

>>>>

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, cache=FALSE}
##It is assumed your working directory is "~/ampad-DiffExp/gene_level_analysis"
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(glmnet)
library(synapser)
library(knitr)
library(doParallel)
library(foreach)
library(githubr)

cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
# Source modified utility functions from limma and sva package
source('../utilityFunctions/parallelDuplicateCorrelation.R')
source('../utilityFunctions/irwsva.build.R')
source('../utilityFunctions/f.pvalue.R')
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

### 2019-09-19 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
Final Regress

---
title: Covariate Analysis of ROSMAP Reprocessed counts Regressing out Diagnosis as well for TWAS

author: 'JKG - Adapted from: Thanneer Perumal'
output: html_notebook
editor_options:
  chunk_output_type: console
---
Date of analysis update: "`r date()`"

@@

### Load Libraries
```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## It is assumed your working directory is where this file
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(synapser)
library(knitr)
library(doParallel)
library(foreach)
cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

>>>>

---
title: Covariate Analysis of ROSMAP Reprocessed counts Regressing out Diagnosis as well for TWAS
author: 'JKG - Adapted from: Thanneer Perumal'
output: html_notebook
editor_options:
  chunk_output_type: console
---
Date of analysis update: "`r date()`"

@@

### Load Libraries
```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## It is assumed your working directory is where this file
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(synapser)
library(knitr)
library(doParallel)
library(foreach)
library(githubr)

cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```
